### 2015-08-14 documentation/paper.tex

\documentclass[	a4paper,
			11pt,
			oneside,
			parskip]{scrartcl}
\usepackage{package/ownstil}
\usepackage{package/owncmd}

\begin{document}

\section*{Zielstellung und Rahmenbedingungen}

% ---------------------------------------------------------------------------------------------- %
%	
% ---------------------------  ------------------------------ %
%
% ---------------------------------------------------------------------------------------------- %
\clearpage
\section*{

% ---------------------------------------------------------------------------------------------- %
%	
% --------------------------------------  ------------------------------------------ %
%
% ---------------------------------------------------------------------------------------------- %
\clearpage
\section*{}

% ---------------------------------------------------------------------------------------------- %
%	
% ------------------------------  --------------------------------- %
%
% ---------------------------------------------------------------------------------------------- %
\clearpage
\section*{}

\clearpage
\section*{Zusammenfassung \& Fazit}

\end{document}